### 2022-01-14 New-Manuscript/sections/mdp_model.tex
phase 1 works phase 2 doesnt
modifications

\subsubsection{Auxiliary Variables}
\begin{itemize}
	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
	\item $\hat{ul}_{p \in p\_co}$ - post-decision unit leftover at period 1
	\item $ulb_{p \in p\_co}$ - binary variable to enforce $ul$ variable without objective function
	\item $\hat{uu}_{tp}$ - post-decision units used
	\item $\hat{pw}_{mdkc}$ - post-decision patients waiting
	\item $\hat{ps}_{tmdkc}$ - post-decision patients scheduled
	\item $pwt\_d_{mdkc}$ - patients waiting transitioned in complexity
	\item $pwt\_k_{mdkc}$ - patients waiting transitioned in priority
	\item $pst\_d_{tmdkc}$ - patients scheduled transitioned in complexity
	\item $pst\_k_{tmdkc}$ - patients scheduled transitioned in priority
\end{itemize}
\subsubsection{Auxiliary Variable Definition}
\label{auxiliary constraints}
\begin{alignat}{10}
	& \hat{uu}_{tp} 
		&& =  \sum_{mdkc} U_{pdc} \hat{ps}_{tmdkc} \quad
		&& \forall tp \\ 
	& \hat{pw}_{mdkc} 
		&& = pw_{mdkc} - \sum_{t} sc_{tmdkc} \quad 
		&& \forall mdkc \\ 
	& \hat{ps}_{tmdkc} 
		&& = ps_{tmdkc} + sc_{tmdkc} + 
		\sum_{t} rsc_{tt'mdkc} - \sum_{t'} rsc_{tt'mdkc} \quad 
		&& \forall tmdkc \\
	& pwt\_d_{mdkc} 
		&& = ptp\_{dc} * \hat{pw}_{mdkc} \quad
		&& \forall mdkc \\
	& pwt\_k_{mdkc} 
		&& = ptp\_{kc} * \hat{pw}_{mdkc} \quad
		&& \forall mdkc \\
	& pst\_d_{tmdkc} 
		&& = ptp\_{dc} * \hat{ps}_{tmdkc} \quad
		&& \forall tmdkc \\
	& pst\_k_{tmdkc} 
		&& = ptp\_{kc} * \hat{ps}_{tmdkc} \quad
		&& \forall tmdkc
\end{alignat}

@@

\begin{equation}\begin{alignedat}{10}
		& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
		\overbrace{ \sum_{mdkc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
			cost of waiting}  + 
		\overbrace{
			\sum_{tmdkc} cs_{tk} (sc_{tmdkc})
		}^\text{Prefer earlier appointments} \\ 
		&	&&  +
		\overbrace{
			\sum_{
				\substack{tt`mdkc \\ t' > t}} 
			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
		\overbrace{ 
			\sum_{
				\substack{tt`mdkc \\ t' < t}}
			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
		M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

>>>>

\subsubsection{Auxiliary Variables}
\begin{itemize}
	\item $\vec{uv} = uv_{tp}$ - goal variable, violation on number of resources used for period $t$, of resource $p$
	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
	\item $\hat{ul}_{p \in p\_co}$ - post-decision unit leftover at period 1
	\item $ulb_{p \in p\_co}$ - binary variable to enforce $ul$ variable without objective function
	\item $\hat{uu}_{tp}$ - post-decision units used
	\item $\hat{pw}_{mdkc}$ - post-decision patients waiting
	\item $\hat{ps}_{tmdkc}$ - post-decision patients scheduled
	\item $pwt\_d_{mdkc}$ - patients waiting transitioned in complexity
	\item $pwt\_k_{mdkc}$ - patients waiting transitioned in priority
	\item $pst\_d_{tmdkc}$ - patients scheduled transitioned in complexity
	\item $pst\_k_{tmdkc}$ - patients scheduled transitioned in priority
\end{itemize}
\subsubsection{Auxiliary Variable Definition}
\label{auxiliary constraints}
\begin{alignat}{10}
	& \hat{uu}_{tp} 
		&& =  \sum_{mdkc} U_{pdc} \hat{ps}_{tmdkc} \quad
		&& \forall tp \\ 
	& \hat{pw}_{mdkc} 
		&& = pw_{mdkc} - \sum_{t} sc_{tmdkc} \quad 
		&& \forall mdkc \\ 
	& \hat{ps}_{tmdkc} 
		&& = ps_{tmdkc} + sc_{tmdkc} + 
		\sum_{t} rsc_{tt'mdkc} - \sum_{t'} rsc_{tt'mdkc} \quad 
		&& \forall tmdkc \\
	& pwt\_d_{mdkc} 
		&& = ptp\_{dc} * \hat{pw}_{mdkc} \quad
		&& \forall mdkc \\
	& pwt\_k_{mdkc} 
		&& = ptp\_{kc} * ( \hat{pw}_{mdkc} + pwt\_d_{md-1kc} - pwt\_d_{mdkc} )  \quad
		&& \forall mdkc \\
	& pst\_d_{tmdkc} 
		&& = ptp\_{dc} * \hat{ps}_{tmdkc} \quad
		&& \forall tmdkc \\
	& pst\_k_{tmdkc} 
		&& = ptp\_{kc} * ( \hat{ps}_{tmdkc} + pst\_d_{tmd-1kc} - pst\_d_{tmdkc} )  \quad
		&& \forall tmdkc
\end{alignat}

@@

\begin{equation}\begin{alignedat}{10}
		& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
		\overbrace{ \sum_{mdkc} cw_{k} (\hat{pw}_{mdkc}) }^\text{
			cost of waiting}  + 
		\overbrace{
			\sum_{tmdkc} cs_{tk} (sc_{tmdkc})
		}^\text{Prefer earlier appointments} \\ 
		&	&&  +
		\overbrace{
			\sum_{
				\substack{tt`mdkc \\ t' > t}} 
			(cs_{t'-t, k} + cc) * (rsc_{tt'mdc})}^\text{Bad Reschedule} - 
		\overbrace{ 
			\sum_{
				\substack{tt`mdkc \\ t' < t}}
			(cs_{t-t', k} - cc) * (rsc_{tt'mdc})}^\text{Good Reschedule} + 
		cv \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}
